Inquires in Racial and Sexual Disparities among Chicago Police Department

### 2024-02-15 paper/paper.qmd
Adding test and sim script and removing redundant files

## Disparities in police awards 
```{r}
#| label: tabl-two
#| echo:  false
#| warning: false
#| message: false
 # run script **name

organized_table_2 <- read.csv("~/Police-Award-Nomination-Paper-Reproduction/data/analysis_data/table_2_data.csv")

```
```{r}
table_content <- readLines("~/Police-Award-Nomination-Paper-Reproduction/table_2.tex", warn = FALSE)

# Print the contents of the table
cat(table_content, sep = "\n")
```

>>>>

## Disparities in police awards 
```{r}
#| label: tabl-two
#| echo:  false
#| warning: false
#| message: false
# run script table_2_regression in script file first
# regression table

 stargazer(fe_reg_black,fe_reg_female, fe_reg_black_female,fe_reg_blackxfemale, header=FALSE,
          omit =c("hisp", "asian", "natam", "birth_year", "tenure", "tenure2",
          "tenure3", "L_cmpl_civ", "L_cmpl_civ2", "L_cmpl_civ3",
          "L_arrest_total", "L_arrest_total2","L_arrest_total3","L_trr_new",
          "L_trr_new2","L_trr_new3"),
          omit.stat=c("f", "rsq","adj.rsq"),
          add.lines=list(c("Control for"),
                         c("Cohort", "Yes", "Yes", "Yes", "Yes"), 
                         c("Year",  "Yes", "Yes", "Yes", "Yes"), 
                         c("Demographics", " ", " ", "Yes", "Yes"),
                         c("Policing activities", "", "", "Yes", "Yes"),
                         c("Reference group mean",round(mean_white, digits = 2), 
                           round(mean_female_0, digits = 2), 
                           round(mean_white_female_0, digits = 2), 
                           round(mean_white_female_0, digits = 2))), 
          type = 'text', star.cutoffs = NA, omit.table.layout = "n")
```

$$ 
\text{Award_perf}_{it} = \beta_0 + \beta_1 \text{Black}_{it} + \beta_2 \text{Hisp}_{it} + \beta_3 \text{Asian}_{it} + \beta_4 \text{Natam}_{it} + e_{it}
$$
$$
\text{Award_perf}_{it} = \beta_0 + \beta_1 \text{female}_{it}
$$

$$
\text{Award_perf}_{it} = \beta_0 + \beta_1 \text{Black}_i + \beta_2 \text{Female}_i + \beta_3 \text{Black}\times\text{Female}_{it} + \text{other confounding variables}
$$
